\section{Related tools}

There are two tools related to Mezuro: SonarQube\footnote{\url{sonarqube.org}}
and Code Climate\footnote{\url{codeclimate.com}}. SonarQube offers a platform
to manage software quality by using plugins through a
library\footnote{\url{docs.sonarqube.org/display/PLUG/Plugin+Library}}.
%
At its most basic version, it classifies code problems and evaluates simple
coverage metrics in several languages. SonarQube core is licensed as LGPLv3,
however, its best plugins are paid and proprietary, such as the C/C++
analyzer\footnote{\url{sonarsource.com/why-us/products/codeanalyzers/sonarcfamilyforcpp.html}}.

Code Climate is a tool that analyzes source code hosted in a Git server, and it
has support for several programming languages and frameworks. The analysis
looks for code smells in the code and classifies them based on aspects such as
size of methods and code duplication. Based on the smells that the tool
identifies, the project under analysis will receive a grade ranging from A to
F. Keep in mind that what is tagged as a code smell sometimes might not be a
real problem, since it could be the best solution for the given scenario.

% novo parágrafo
% foco nos pontos fortes do mezuro em relaçao ao sonarqube e codeclimate
Mezuro has three main strenghts regarding the tools mentioned. First, it stills
is the only complete FOSS alternative to monitor source code metrics, unlike
SonarQube, or Code Climate. Second, Mezuro has the % parentêse?
differential to continuously generate reviews about the project: the user
schedules the analysis and follows metric results evolution over time. Third,
Mezuro allows a level of metrics configuration and composition that is not
available in the other two tools, and that gives the control of the formula
used to evaluate the source code.

These differences brings interesting scenarios for users. For instance, if a
community already knows the project requirements, and has access to multiple
tools that are suitable, they can use source code results presented by Mezuro to
lead their choice, since the data is public.

% antigo:
% Such as SonarQube, Code Climate also is not fully FOSS and, therefore, Mezuro
% still is the only complete FOSS alternative to monitor source code metrics.
% %
% Mezuro has the differential to continuously generate reviews about the project:
% the user schedules the analysis and follows metric results evolution over time.
% Results of each analysis are public, what allows greater transparency between
% the developer and the community that uses the software. Thereby, the
% maintainers can decide if the given solution meets the source code quality
% requirements. Another example, the community already knows the project
% functionally and, in a good scenario where there are more than one project with
% the same functionalities, the maintainers choose the one with the best metrics.
